ESRC SDAI Application

### 2019-06-12 case_for_support.tex
X

\subsection{A description of victims and perpetrators}

\subsection{Association with other criminal behaviours}

It is common that individuals are more likely to be a victim of crime if they have previously been a victim of crime, and if they have perpetrated crimes. It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the victim of crimes. We will use our datasets to improve our understanding of the temporal patterns of victims and perpetrators, particularly around domestic abuse. The high level of detail in the CSEW allows us to examine the comorbidity of domestic abuse with other crimes during the previous year, and since the age of 16. It also contains information about  multiple members of the household. This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime. By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.

The scope of the WMP dataset across time lets us take these questions further, by looking at the order in which events occur and at patterns across many years. We can examine whether a recorded victim of domestic abuse was previously recorded as a victim in other crimes, and if they were subsequently a victim of other criminal behaviours. Identifying risk factors is crucial for police services who want to identify individuals at risk of being future victims, so that they can target interventions and give the best advice possible to reduce an individual's risk. In addition, we can measure the relationship between experiencing domestic abuse, and the likelihood of being recorded as a suspect in other crimes. It is possible that some criminal behaviour is a precursor to experiencing domestic abuse whilst others follow it. For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.

?

@@

The WMP data are cases that have been reported to the police. The CSEW allows an estimate of the prevalence of domestic abuse. The discrepancy between the two datasets allows us to estimate the reporting gap. We first explore the characteristics of offenders and victims. \textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}

@@

@@

\subsection{Predicting serious harm}
Separation is one of the biggest predictors of abuse resulting in serious injury. \textit{Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures. If not, we can still use info on location + breaches of non-molestation orders?}

\subsection{Collateral damage}

@@

@@

\subsection{The Temporal Course of Domestic Abuse OR Reporting behaviour and temporal dynamics}

>>>>

@@

The WMP data are cases that have been reported to the police. The CSEW allows an estimate of the prevalence of domestic abuse. The discrepancy between the two datasets allows us to estimate the reporting gap. We first explore the characteristics of offenders and victims.

@@

\subsubsection{A description of victims and perpetrators}

\textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}

\subsubsection{Association with other criminal behaviours}

It is common that individuals are more likely to be a victim of crime if they have previously been a victim of crime, and if they have perpetrated crimes. It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the victim of crimes. We will use our datasets to improve our understanding of the temporal patterns of victims and perpetrators, particularly around domestic abuse. The high level of detail in the CSEW allows us to examine the comorbidity of domestic abuse with other crimes during the previous year, and since the age of 16.

The scope of the WMP dataset across time lets us take these questions further, by looking at the order in which events occur and at patterns across many years. We can examine whether a recorded victim of domestic abuse was previously recorded as a victim in other crimes, and if they were subsequently a victim of other criminal behaviours. Identifying risk factors is crucial for police services who want to identify individuals at risk of being future victims, so that they can target interventions and give the best advice possible to reduce an individual's risk. In addition, we can measure the relationship between experiencing domestic abuse, and the likelihood of being recorded as a suspect in other crimes. It is possible that some criminal behaviour is a precursor to experiencing domestic abuse whilst others follow it.

@@

\subsection{Predicting serious harm}

Separation is one of the biggest predictors of abuse resulting in serious injury. \textit{Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures. If not, we can still use info on location + breaches of non-molestation orders?}

For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.

\subsection{Collateral damage}
It also contains information about  multiple members of the household. This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime. By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.

@@

Australia study on domestic abuse and proximity to fixed-odds betting terminals, and the one on offlicences.

@@

\subsection{The Temporal Course and the Decision to Report}
